---
title: "R Notebook"
output: html_notebook
---

 

```{r}
dataCredit <- Credit
head(dataCredit)
```
#Mean of rating
```{r}
mean(dataCredit$Rating)

```
#Mean of Cards
```{r}
mean(dataCredit$Cards)
```
#Mean of Age
```{r}
mean(dataCredit$Age)
```
#Median of Rating
```{r}
median(dataCredit$Rating)
```
#Median of Cards
```{r}
median(dataCredit$Cards)
```
#Median of Age
```{r}
median(dataCredit$Age)
```
```{r}
library(lsr)

```

```{r}
install.packages("lsr")
```
```{r}
library(lsr)
```
#Mode of gender
```{r}
modeOf(dataCredit$Gender)
```
#Mode Of Student
```{r}
modeOf(dataCredit$Student)
```

#Mode of Married
```{r}
modeOf(dataCredit$Education)
```
#Sample 10 Percentiles of Educate
```{r}
quantile(x = dataCredit$Education, probs=0.1 )
```
#Sample 37 Percentiles of Educate
```{r}
quantile(x = dataCredit$Education, probs=0.37 )
```
#Sample 91 Percentiles of Educate
```{r}
quantile(x = dataCredit$Education, probs=0.91 )
```
#quartile
```{r}
quantile(x = dataCredit$Balance, probs= c(0.25, 0.50, 0.75))
```
```{r}
boxplot(dataCredit$Balance)
```

```{r}
boxplot(dataCredit$Balance, horizontal= TRUE)
```
#Correlation Limit & Rating
```{r}
newData <- data.frame(limit = dataCredit$Limit, rating= dataCredit$Rating)
newData
```
#Correlation Age & Cards
```{r}
newData <- data.frame(age = dataCredit$Age, cards= dataCredit$Cards)
newData
```

#Correlation Income & Education
```{r}
newData <- data.frame(income = dataCredit$Income, Education= dataCredit$Education)
newData
```

#Plot limit & rating
```{r}
newData <- data.frame(limit = dataCredit$Limit, rating= dataCredit$Rating)
newData
```
```{r}
plot(newData$limit, newData$rating)
```

#Plot Age & cards
```{r}
newData <- data.frame(age = dataCredit$Age, cards= dataCredit$Cards)
newData
```
```{r}
plot(newData$age, newData$cards)
```
#Plot Income & Educate
```{r}
newData <- data.frame(income = dataCredit$Income, Education= dataCredit$Education)
newData
```
```{r}
plot(newData$income, newData$Education)
```




